### 2014-08-11 Studies/2012_Chicago/Report/Chicago_Fire.tex
Chicago: minor update timeline

\begin{table}
\centering
\captionof{table}[Abridged NIOSH approximate fire event timeline]{Abridged NIOSH approximate fire event timeline~\cite{NIOSH:Bowyer}}\label{tab:fire_info}
\begin{tabular}{cl}
\toprule[1.5pt]
Incident Time              &  Fire Behavior / Fireground Operation                                                                                                    \\
{[hh:mm:ss]}               &                                                                                                                                          \\
\midrule
\multirow{2}{*}{17:15:00}  &  \multirow{2}{*}{\parbox{10cm} {Reported working fire with heavy smoke coming from the front and rear of the structure's attic.}}        \\ 
                           &                                                                                                                                          \\[.25cm] %blank rows exist for wrapping text. # of blanks is 1 less than number of rows
\multirow{2}{*}{17:16:00}  &   \multirow{2}{*}{\parbox{10cm} {Dispatch for a ``Still'' alarm - two engine companies, two truck companies, and a battalion chief.}}    \\
                           &                                                                                                                                          \\[.25cm]
\multirow{2}{*}{17:20:00}  &  \multirow{2}{*}{\parbox{10cm} {Attic windows break - heavy smoke out of front attic window and heavy smoke and fire out of rear.}}      \\
                           &                                                                                                                                          \\[.25cm] 
17:21:00                   &  E123 captain and firefighter on second floor with 1\sfrac{3}{4}-inch hoseline.                                                          \\[.25cm]
17:21:30                   &  First floor exterior porch door opened.                                                                                                 \\[.25cm]
\multirow{2}{*}{17:23:00}  &  \multirow{2}{*}{\parbox{10cm} {Heavy fire report in rear stairwell and enclosed porch. No response from E123 captain or firefighter.}}  \\
                           &                                                                                                                                          \\[.25cm]
17:24:00                   &   Water applied to attic from the rear exterior position.                                                                                \\[.25cm]
17:25:00                   &   SQ5 makes entry through front of structure.                                                                                            \\[.25cm]
17:27:00                   &   After hearing a Mayday call from SQ5, IC calls a Mayday.                                                                               \\[.25cm]
17:29:00                   &   E123 captain carried out of structure.                                                                                                 \\
\bottomrule[1.25pt]
\end{tabular}\par
\end{table}

>>>>

\begin{table}
\centering
\captionof{table}[Abridged NIOSH approximate fire event timeline]{Abridged NIOSH approximate fire event timeline~\cite{NIOSH:Bowyer}}\label{tab:fire_info}
\begin{tabular}{cl}
\toprule[1.5pt]
Incident Time              &  Fire Behavior / Fireground Operation                                                                                                    \\
{[hh:mm:ss]}               &                                                                                                                                          \\
\midrule
\multirow{2}{*}{17:16:00}  &   \multirow{2}{*}{\parbox{10cm} {Dispatch for a ``Still'' alarm - two engine companies, two truck companies, and a battalion chief.}}    \\
                           &                                                                                                                                          \\[.25cm]
\multirow{2}{*}{17:17:00}  &  \multirow{2}{*}{\parbox{10cm} {On-scene report of a working fire with heavy smoke coming from the front and rear of the structure's attic.}}        \\ 
                           &                                                                                                                                          \\[.25cm] %blank rows exist for wrapping text. # of blanks is 1 less than number of rows
\multirow{2}{*}{17:20:00}  &  \multirow{2}{*}{\parbox{10cm} {Attic windows break - heavy smoke out of front attic window and heavy smoke and fire out of rear.}}      \\
                           &                                                                                                                                          \\[.25cm] 
17:21:00                   &  E123 captain and firefighter on second floor with 1\sfrac{3}{4}-inch hoseline.                                                          \\[.25cm]
17:21:30                   &  First floor exterior porch door opened.                                                                                                 \\[.25cm]
\multirow{2}{*}{17:23:00}  &  \multirow{2}{*}{\parbox{10cm} {Heavy fire report in rear stairwell and enclosed porch. No response from E123 captain or firefighter.}}  \\
                           &                                                                                                                                          \\[.25cm]
17:24:00                   &   Water applied to attic from the rear exterior position.                                                                                \\[.25cm]
17:25:00                   &   SQ5 makes entry through front of structure.                                                                                            \\[.25cm]
17:27:00                   &   After hearing a Mayday call from SQ5, IC calls a Mayday.                                                                               \\[.25cm]
17:29:00                   &   E123 captain carried out of structure.                                                                                                 \\
\bottomrule[1.25pt]
\end{tabular}\par
\end{table}
